Transfer of Learned Opponent Models in Zero Sum Games

### 2020-01-16 Report/draft_report_v1.Rmd
citation added

---
title             : "Transfer of Learned Opponent Models in Zero Sum Games"

shorttitle        : "Draft-1"

@@

# bibliography      : ["r-references.bib"]

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes   :
  - \usepackage[document]{ragged2e}
---

@@

```{r texreport}
# texreport <- function(object,effect.name,...) UseMethod("texreport")
# texreport.default <- function(object,effect.name,...) return(NULL)
# 
# texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
#   if(effect.name %in% rownames(object$coefficients)) {
#     tab <- object$coefficients
#     estimate <- tab[effect.name,"Estimate"]
#     se <- tab[effect.name,"Std. Error"]
#     Tval <- tab[effect.name,"t value"]
#     df <- tab[effect.name,"df"]
#     pval <- tab[effect.name,"Pr(>|t|)"]
#     if(pval < .001) ptext <- "$p < .001$" else {
#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
#       }
#     }
#     txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
#     txt <- paste(txt,ptext,sep="")
#   } else {
#     txt <- "error"
#   }
#   txt
# }

# texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
#   if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
#     epsilon <- object$pval.adjustments[effect.name,"HF eps"]
#     pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
#   } else {
#     epsilon <- 1
#     pval <- object$univariate.tests[effect.name,"Pr(>F)"]
#   }
#   df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
#   df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
#   Fval <- object$univariate.tests[effect.name,"F"]
#   etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
#   # generate latex output
#   if(pval < .001) ptext <- "$p < .001$" else {
#     if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
#       ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
#     }
#   }
#   txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
#   if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
#   txt <- paste(txt,ptext,sep="")
#   txt
# }
# 
# texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
#   if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
#     df1 <- object$df
#     df2 <- object$df.residual
#     Fval <- (object$SSPH/df1)/(object$SSPE/df2)
#     pval <- 1-pf(Fval,object$df,object$df.residual)
#     etasq <- object$SSPH/(object$SSPH + object$SSPE)
#     # generate latex output
#     if(pval < .001) ptext <- "$p < .001$" else {
#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
#       }
#     }
#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
#     if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
#     txt <- paste(txt,ptext,sep="")
#   } else {
#     txt <- "error"
#   }
#   txt
# }
# 
# texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
#   if(effect.name %in% rownames(object)) {
#     pval <- object[effect.name,"p-value"]
#     if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
#     df1 <- object[effect.name,"numDF"]
#     df2 <- object[effect.name,"denDF"]
#     Fval <- object[effect.name,"F-value"]
#     #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
#     # generate latex output
#     if(pval < .001) ptext <- "$p < .001$" else {
#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
#       }
#     }
#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
#     #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
#     txt <- paste(txt,ptext,sep="")
#     txt
#   }
# }
# 
# texreport.anova <- function(object,effect.name,effect.size=FALSE) {
#   if(effect.name %in% rownames(object)) {
#     pval <- object[effect.name,"Pr(>F)"]
#     df1 <- object[effect.name,"NumDF"]
#     df2 <- object[effect.name,"DenDF"]
#     Fval <- object[effect.name,"F.value"]
#     #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
#     # generate latex output
#     if(pval < .001) ptext <- "$p < .001$" else {
#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
#       }
#     }
#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
#     #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
#     txt <- paste(txt,ptext,sep="")
#     txt
#   }
# }

```{r read-data,warning=FALSE}
# source("R/readData.R")
# demo_exit <-  read.csv("data/demographics_and_exit_clean.csv")
# trial_data <- read.csv("data/trial_data_clean.csv")
# trial_data$trial <- 1:100
```

@@

# Introduction
Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008). Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge. More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation. This typically human skill has so far eluded modern ai agents. Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games. Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains. Lake et al.(2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.

@@

@@

>>>>

---
title             : "Transfer of Learned Opponent Models in Zero Sum Games"
shorttitle        : "Draft-1"

@@

bibliography      : ["Mendeley.bib"]
csl               : "apa-6th-edition.csl"

@@

# documentclass     : "apa6"
# classoption       : "man"
output            : papaja::apa6_pdf
header-includes   :
  - \shorttitle{}
---

@@

@@

# Introduction
Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence [@taylor2008transfer]. Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge. More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation. This typically human skill has so far eluded modern ai agents. Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games. Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains. [@lakeBuildingMachinesThat2017] @lake2017building argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.

@@

\newpage

@@

\newpage

# References

```{r create_r-references}
# r_refs(file = "OM_transfer.bib")

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2020-01-16 Report/draft_report_v1.tex
citation added

Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008). Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge. More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation. This typically human skill has so far eluded modern ai agents. Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games. Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains. Lake et al.(2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.

@@

>>>>

Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence ({\textbf{???}}). Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge. More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation. This typically human skill has so far eluded modern ai agents. Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games. Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains. (Lake, Ullman, Tenenbaum, \& Gershman, n.d.) ({\textbf{???}}) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.

@@

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-lakeBuildingMachinesThat2017}{}%
Lake, B. M., Ullman, T. D., Tenenbaum, J. B., \& Gershman, S. J. (n.d.). Building machines that learn and think like people. \emph{Behavioral and Brain Sciences}, \emph{40}. \url{https://doi.org/10.1017/S0140525X16001837}

\endgroup
